%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Philips Respironics} % Organization
{Pittsburgh, PA} % Location
{Aug. 2018 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item 
{
    \href{https://www.usa.philips.com/healthcare/product/HCNOCTN447/dreamstation-cpap-bi-level-therapy-systems}{\color{RoyalBlue}DreamStation 2} 
    (coming soon).
    \begin{itemize}
        \item Contributed to various bug fixes on the device writing in C/C++ for a microprocessor running a RTOS. 
        \item Created WPF .Net core application to upgrade the device using STM DFU protocol. 
    \end{itemize} 
}
\item 
{
    \href{https://www.usa.philips.com/c-e/smartsleep/deep-sleep-headband.html}{\color{RoyalBlue}SmartSleep Headband} 
    \begin{itemize}
        \item Contributed to Embedded Firmware running FreeRTOS on STMF4. 
        \item Maintained .Net framework desktop application for interacting with the device.
    \end{itemize} 
}
\item 
{
    \href{https://www.usa.philips.com/healthcare/product/HCNOCTN350/simplygo-mini-portable-oxygen-concentrator-poc}{\color{RoyalBlue}Next Gen Simply Go} 
    \begin{itemize}
        \item Used STM32F4 Development board to prototype various sensors for the new Nano Device.
        \item Implemented valve control algorithms to produce 90\% oxygen.
        \item Worked closely with Mechanical and Electrical Engineers. 
    \end{itemize} 
}
\item 
{
    \textbf{Agile/Supervisor roles} 
    \begin{itemize}
        \item Was placed in charge of three interns to create a new application using \href{https://avaloniaui.net/}{\color{RoyalBlue}Avalonia}.
        \item Scrum Master on various teams. 
        \item Received Agile Transformation Pioneer for helping convert a team of 70 people into multiple scrum teams following \href{https://www.scaledagileframework.com/}{SAFe} practices.
    \end{itemize} 
}
\item 
{
    \textbf{Initiative SVN to Gitlab} Helped carry out a transition to Git from SVN for 70 plus developers. Provided training and conducted cost benefit analysis 
    of transitioning. Worked with other team members to get buy in and convince management to let us carry out the initiative.
}
\item 
{
    \textbf{Initiative Artifactory} Identified a need for Artifact management after transition to Git. Started an initiative to add Artifactory to our CI/ CD pipeline. 
    This required requirements generation, project planning, cost benefit analysis. Team now has an Artifactory instance that supports: Pip, Nuget, and Conan packages.
}
\end{cvitems}
}


%------------------------------------------------    

\cventry
{Software Engineer} % Job title
{IQ Inc} % Organization
{Pittsburgh, PA } % Location
{July 2017 - Aug. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item 
{
    \textbf{Hitachi}
    \begin{itemize}
        \item Worked at Hitachi developing automatic train control systems in C/C++.
        \item Integrated Unit Tests into legacy code system using Google Test and Google Mock frameworks.
    \end{itemize} 
}
\item 
{
    \textbf{ALung}
    \begin{itemize}
        \item Preformed formal verification testing for products like hemolung. 
    \end{itemize} 
}  
\end{cvitems}
}

%------------------------------------------------



\end{cventries}